% Acknowledgements

\pdfbookmark[1]{Acknowledgements}{Acknowledgements} % Bookmark name visible in a PDF viewer

\begin{flushright}{\slshape
We have seen that computer programming is an art, \\
because it applies accumulated knowledge to the world, \\
because it requires skill and ingenuity, and especially \\
because it produces objects of beauty.} \\ \medskip
\fullcite{knuth2007computer}
\end{flushright}

\bigskip

%----------------------------------------------------------------------------------------

\begingroup

\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax

\chapter*{Acknowledgements} % Acknowledgements section text

This thesis could not have come about without the help of many people.
Foremost, I wish to thank my supervisors, Professor Emeritus Kikuko Nishina and Professor Masao Murota, for their support and guidance.
The most significant contributions that made this research possible were the work of the informally named ``Asunaro Group'' led by Kikuko Nishina.
I thank Takeshi Abekawa, Yutaka Yagi, Taizan Suzuki, and Liang Fu for their work on the Asunaro, Natsume, and Nutmeg systems.
This work would not be possible without them.

Next, I would like to thank Terry Joyce for considerable help with proofreading this thesis.

I am also indebted to Hilofumi Yamamoto, whose invaluable comments and support led to several ideas present in this thesis, and to Minoru Nakayama, Kayoko Nohara, and Hiroyuki Akama for their patience and feedback during the writing of this thesis.

Frequent research meetings with Andrej Bekeš, Irena Srdanović, and Kikuko Nishina also provided a place for discussions that influenced some of the ideas presented within the thesis.

I would also like to thank the members of Murota Lab, as well as the Nishina Lab members before them, for their warm feedback and support during the writing of this thesis.

I would like to thank all the research participants who gave so willingly of their time to the system evaluations.

And finally, I gratefully appreciate the financial support provided by MEXT that made it possible to focus on my studies and complete this thesis.

\vspace{1cm}

\hfill Bor Hodošček\\

\hfill August \hspace{-1em} \ordinalnum{8}, 2013\\

\hfill Tokyo

% I would also like to thank my former supervisor at the University of Ljubljana, Professor Andrej Bekeš, who often took time off from his sabbatical at the Tokyo Institute of Technology to help flesh out new ideas and who also gave considerable moral encouragement.
% Additionally, I would also like to thank Associate Professors Hiroyuki Akama and Masao Murota, who gave me invaluable comments and warm encouragement during the writing of this thesis.
%I would also like to thank fellow colleagues Cui

%Finally, I gratefully appreciate the financial support provided by MEXT that made it possible to focus on my studies and complete my thesis.



% \noindent Many thanks to everybody who already sent me a postcard!\\
%
% \noindent Regarding the typography and other help, many thanks go to Marco Kuhlmann, Philipp Lehman, Lothar Schlesier, Jim Young, Lorenzo Pantieri and Enrico Gregorio\footnote{Members of GuIT (Gruppo Italiano Utilizzatori di \TeX\ e \LaTeX )}, J\"org Sommer, Joachim K\"ostler, Daniel Gottschlag, Denis Aydin, Paride Legovini, Steffen Prochnow, Nicolas Repp, Hinrich Harms, Roland Winkler,  and the whole \LaTeX-community for support, ideas and some great software.
%
% \bigskip
%
% \noindent\emph{Regarding \mLyX}: The \mLyX\ port was intially done by
% \emph{Nicholas Mariette} in March 2009 and continued by
% \emph{Ivo Pletikosi\'c} in 2011. Thank you very much for your work and the contributions to the original style.

\endgroup
